The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-30 ms.Rmd
Add bioclim reference.

Modules are simply R function definitions, with a set of required inputs and outputs.
For example, the`Bioclim` module, which uses the `raster` R package [@raster] to download the widely used bioclim [] covariate layers in the correct format, is defined as:

@@

@Feng2015 constructed a MaxEnt species distribution model for nine-banded armadillo in the USA using presence-only data on the species' current distribution, and the bioclim [] set of environmental correlates.
This model was then used to predict areas in the Americas which may be suitable for the species to become established.

@@

```{r fengworkflow, eval = TRUE, results = 'hide', message = FALSE}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 1000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))

>>>>

Modules are simply R function definitions, with a set of required inputs and outputs.
For example, the`Bioclim` module, which uses the `raster` R package [@raster] to download the widely used bioclim [@Hijmans2005] covariate layers in the correct format, is defined as:

@@

@Feng2015 constructed a MaxEnt species distribution model for nine-banded armadillo in the USA using presence-only data on the species' current distribution, and the bioclim [@Hijmans2005] set of environmental correlates.
This model was then used to predict areas in the Americas which may be suitable for the species to become established.

@@

```{r fengworkCaptions, eval = TRUE, echo = FALSE}
fengworkcap <- '
  Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence (darker blue showing higher probability of occurrence).
  White areas are masked due to being marine or due the MESS mask [@Elith2010]
'

```{r fengworkflow, eval = TRUE, results = 'hide', message = FALSE, fig.cap = fengworkcap}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 1000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))
